### 2013-11-22 loadClean.Rmd
Regression models updated with perceived gini

df <- subset(lits2, select=c("SerialID","weight",
                             "cntry","q309",
                             "sex","age",
                             "pov.log.social",
                             "pov.log.individual",
                             "socialism","incsour3",
                             "edu2",
                             "group_analysis",
                             "income2",
                             "poverty",
                             "future.diff","past.diff"
                             ))
names(lits1)[2] <- "SerialID"
names(lits1)[1165] <- "weight"

>>>>

df <- subset(lits2, select=c("SerialID","weight",
                             "cntry","q309",
                             "sex","age",
                             "pov.log.social",
                             "pov.log.individual",
                             "socialism","incsour3",
                             "edu2",
                             "group_analysis",
                             "income2",
                             "poverty",
                             "crise",
                             "future.diff","past.diff"
                             ))
names(lits1)[2] <- "SerialID"
names(lits1)[1165] <- "weight"

### 2013-11-22 regressionModelling.Rmd
Wave 2006 also included. Numerous minor corrections to data munging also for 2010 data. Nothing major I think. Well, low education is currently covering only uneducated individuals.
Changed the toc font size in css
Regression models updated with perceived gini

`log of changes`

date      comment
--------  -------------------
20131103  Non multi-level logistic regression done but not interpret yet. Bivariate multilevel models the same. Multivariate multilevel models running over night.
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Model names fixed. Multinomial models coming by midday

@@

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.social ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod",
                     "Perceived Gini")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12,
             bisoc.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.individual ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

@@

```{rmultilevelMultiInd}

ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

socVsInc <- glmer(pov.log.socVsInc ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

htmlreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```

@@

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```

>>>>

@@

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
# bisoc.8 <- glmer(pov.log.social ~ perGini+(1|cntry),
#                         family = binomial(logit), data = df.model)
bisoc.9 <- glmer(pov.log.social ~ gdpChange+(1|cntry),
                         family = binomial(logit), data = df.model)
bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.social ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      #"Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod",
                     "Perceived Gini")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          #bisoc.8,
          bisoc.9,bisoc.10,
          bisoc.11,bisoc.12,
          bisoc.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
#biind.8 <- glmer(pov.log.individual ~ perGini+(1|cntry),
#                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpChange+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.13 <- glmer(pov.log.individual ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          #biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Perceived Gini",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

@@

```{rmultilevelMultiInd}
ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)
```

@@

soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

socVsInc <- glmer(pov.log.socVsInc ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

htmlreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)

@@

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
